---
title: "STAT 410 Final Project"
output:
  html_document:
    df_print: paged
---

# CS: GO Utility Usage Analysis


First, we will read in our preprocessed data that contains, round-by-round, the number of times that utility was thrown in particular clusters, and which team won.

```{r}
# Office hours questions
# 1. How do I determine which interaction terms to include? If I want to test a hypothesis - i.e. is this group a good group, I should do it in isolation, right? 
# 2. How do I interpret the results from logistic regression?
# 3. Should I take out the insignificant results? They change the results of other variables, how do I know which to keep and which to take out?


rm(list=ls())
set.seed(42)
library(caret)
library(margins)
library(stargazer)
library(plyr)

df1 <- read.csv("de_mirage_clustered_nade_round_win.csv")
# Remove unimportant columns
df1 <- df1[ , !names(df1) %in% c("X", "file", "round", "Flash_Terrorist_distance_to_centroid", "Flash_CounterTerrorist_distance_to_centroid","HE_Terrorist_distance_to_centroid", "HE_CounterTerrorist_distance_to_centroid", "Smoke_Terrorist_distance_to_centroid","Smoke_CounterTerrorist_distance_to_centroid")]

# Sort columns
df1 <- df1[, order(names(df1))]

# Encode the response variable
df1$winner_side <- ifelse(df1$winner_side == "Terrorist", 0, 1)

# Variable distributions
summary(df1)

# Number of nades thrown in each cluster
colSums(df1)

# Split training/testing data
smp_size <- floor(0.8 * nrow(df1))
train_ind <- sample(seq_len(nrow(df1)), size = smp_size)
train <- df1[train_ind, ]
test <- df1[-train_ind, ]
```

Let's create a model that compares different utility types in their effect on round wins.

```{r}
agg_utility <- df1

# Sum clusters for each respective type of utility and side
agg_utility$Smoke_T <- rowSums(df1[, grep("Smoke_Terrorist*", names(df1))])
agg_utility$Smoke_CT <- rowSums(df1[, grep("Smoke_CounterTerrorist*", names(df1))])
agg_utility$Flash_T <- rowSums(df1[, grep("Flash_Terrorist*", names(df1))])
agg_utility$Flash_CT <- rowSums(df1[, grep("Flash_CounterTerrorist*", names(df1))])
agg_utility$HE_T <- rowSums(df1[, grep("HE_Terrorist*", names(df1))])
agg_utility$HE_CT <- rowSums(df1[, grep("HE_CounterTerrorist*", names(df1))])
mod1 <- glm(winner_side ~ Smoke_T + Smoke_CT + Flash_T + Flash_CT + HE_T + HE_CT, data=agg_utility, family = "binomial")
summary(mod1)
stargazer(mod1, title="Effectiveness of Utility Types",
keep.stat="n", ci=TRUE, ci.level=0.95, single.row=TRUE, type="html")

```
Interestingly, terrorist flashes are the weakest out of all types of utility! HEs are also surprisingly strong.

Now let's look at individual clusters.
```{r}

mydat <- train[ , !(names(train) %in% 
                              c("Flash_CounterTerrorist_distance_to_centroid",
                               "Flash_Terrorist_distance_to_centroid",
                               "HE_CounterTerrorist_distance_to_centroid",
                               "HE_Terrorist_distance_to_centroid",
                               "Smoke_CounterTerrorist_distance_to_centroid",
                               "Smoke_Terrorist_distance_to_centroid"))]
names(mydat) <- gsub("_", ".", names(mydat))
mod1 <- glm(winner.side ~ ., data=mydat, family = "binomial")
summary(mod1)
stargazer(mod1, title="Effectiveness of Utility Positions",
keep.stat="n", ci=TRUE, ci.level=0.95, single.row=TRUE, type="html")
```

Now let's see which clusters are statistically significantly different from the baseline for that team/utility type, where the baseline is all unclustered nades.

```{r}
# Test that common utility positions (clusters) are better than other positions
library(car)
for (nade in c("Flash", "Smoke", "HE")) {
  for (team in c("CounterTerrorist", "Terrorist")) {
    prefix <- paste(nade, "_", team, "_", sep="")
    non_cluster <- paste(prefix, "cluster_.1", sep="")
    clusters <- colnames(df1)[grepl(prefix, colnames(df1)) & !grepl(non_cluster, colnames(df1))]
    for (c in clusters) {
      h0 = paste(non_cluster, "=", c)
      print(paste("Testing", h0))
      pval <- linearHypothesis(mod1, h0)$`Pr(>Chisq)`[2]
      if (pval < 0.05) {
        print("Significant")
      }
    }
  }
}
```

Let's look at the interaction effects of using certain smokes together, as a terrorist.

```{r}
# Terrorist smokes
smoke_df <- df1[,grepl("Smoke", colnames(df1)) & !grepl("CounterTerrorist", colnames(df1)) & !grepl("distance_to_centroid", colnames(df1)) | grepl("winner_side", colnames(df1))]
colnames(smoke_df) = sub("Smoke_Terrorist_", "", colnames(smoke_df))

# Binarize it
smoke_df[,] = ifelse(smoke_df[,] > 0, 1, 0)
t_smoke_group_mod <- glm(winner_side ~ ., data=smoke_df, family = "binomial")
summary(t_smoke_group_mod)
# Pairwise interactions
t_smoke_group_mod2 <- glm(winner_side ~ . 
                          + cluster_3 * cluster_4
                          + cluster_3 * cluster_4 * cluster_5
                          + cluster_1 * cluster_6
                          + cluster_1 * cluster_19
                          + cluster_1 * cluster_14, 
                          data=smoke_df, family = "binomial")
summary(t_smoke_group_mod2)
stargazer(t_smoke_group_mod2, title="Effectiveness of Grouped Smokes",
keep.stat="n", ci=TRUE, ci.level=0.95, single.row=TRUE)


```